\documentclass{beamer}
\usepackage[utf8]{inputenc}

\usetheme{Madrid}
\usecolortheme{default}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{txfonts}
\usepackage{tkz-euclide}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{tabularx}
\usepackage{gvv}
\usepackage{lmodern}
\usepackage{circuitikz}
\usepackage{tikz}
\usepackage{graphicx}

\setbeamertemplate{page number in head/foot}[totalframenumber]

\usepackage{tcolorbox}
\tcbuselibrary{minted,breakable,xparse,skins}



\definecolor{bg}{gray}{0.95}
\DeclareTCBListing{mintedbox}{O{}m!O{}}{%
  breakable=true,
  listing engine=minted,
  listing only,
  minted language=#2,
  minted style=default,
  minted options={%
    linenos,
    gobble=0,
    breaklines=true,
    breakafter=,,
    fontsize=\small,
    numbersep=8pt,
    #1},
  boxsep=0pt,
  left skip=0pt,
  right skip=0pt,
  left=25pt,
  right=0pt,
  top=3pt,
  bottom=3pt,
  arc=5pt,
  leftrule=0pt,
  rightrule=0pt,
  bottomrule=2pt,
  toprule=2pt,
  colback=bg,
  colframe=orange!70,
  enhanced,
  overlay={%
    \begin{tcbclipinterior}
    \fill[orange!20!white] (frame.south west) rectangle ([xshift=20pt]frame.north west);
    \end{tcbclipinterior}},
  #3,
}
\lstset{
    language=C,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    stringstyle=\color{orange},
    commentstyle=\color{green!60!black},
    numbers=left,
    numberstyle=\tiny\color{gray},
    breaklines=true,
    showstringspaces=false,
}
%------------------------------------------------------------

\title
{12.185}
\date{October 1, 2025}
\author 
{AI25BTECH11003 - Bhavesh Gaikwad}



\begin{document}


\frame{\titlepage}
\begin{frame}{Question}
If the rank of a (5$\times$6) matrix $\vec{Q}$ is 4, then which one of the following statements is correct?

\hfill{(EE 2008)}

\begin{itemize}
    \item[a)]$\vec{Q}$ will have four linearly independent rows and four linearly independent columns.
    \item[b)]$\vec{Q}$ will have four linearly independent rows and five linearly independent columns.
    \item[c)]$\vec{Q}\vec{Q}^\top$ will be invertible.
    \item[d)]$\vec{Q}^\top\vec{Q}$ will be invertible 
\end{itemize}

\end{frame}


\begin{frame}[fragile]
    \frametitle{Theoretical Solution}
\textbf{Primary Analysis:}\\
Since rank($\vec{Q}$)=4 $\Rightarrow \; \therefore \vec{Q}$ will have four linearly independent rows and four linearly independent columns.\\

Option-A:\\
Correct Option by Primary Analysis itself.\\

Option-B:\\
Incorrect Option by Primary Analysis itself.\\
\end{frame}


\begin{frame}[fragile]
    \frametitle{Theoretical Solution}
Option C:\\
$\vec{Q}\vec{Q}^\top$ is a $5 \times 5$ matrix.\\
Since $\text{rank}(\vec{Q}^\top) = \text{rank}(\vec{Q}) = 4$,\\
By the Gram matrix rank theorem, $\text{rank}(\vec{A}\vec{A}^\top) = \text{rank}(\vec{A})$ for any matrix $\vec{A}$.\\
Applying this theorem,
\begin{align}
\text{rank}(\vec{Q}\vec{Q}^\top) = \text{rank}(\vec{Q}) = 4
\end{align}
Since $\vec{Q}\vec{Q}^\top$ is a $5 \times 5$ matrix with rank $4 < 5$, it is not full rank and therefore s$\det{(\vec{Q}\vec{Q}^\top)}$ = 0. A square matrix is invertible if and only if it has full rank. Therefore, $\vec{Q}\vec{Q}^\top$ is NOT invertible.

Thus, Incorrect Option.\\
\end{frame}

\begin{frame}[fragile]
    \frametitle{Theoretical Solution}
Option D:\\
$\vec{Q}^\top\vec{Q}$ is a $6 \times 6$ matrix.\\
Since $\text{rank}(\vec{Q}^\top) = \text{rank}(\vec{Q}) = 4$,\\
By the Gram matrix rank theorem, $\text{rank}(\vec{A}^\top\vec{A}) = \text{rank}(\vec{A})$ for any matrix $\vec{A}$.\\
Applying this theorem,
\begin{align}
\text{rank}(\vec{Q}^\top\vec{Q}) = \text{rank}(\vec{Q}) = 4
\end{align}
Since $\vec{Q}^\top\vec{Q}$ is a $6 \times 6$ matrix with rank $4 < 6$, it is not full rank and therefore $\det{(\vec{Q}^\top\vec{Q})}$ = 0. A square matrix is invertible if and only if it has full rank. Therefore, $\vec{Q}^\top\vec{Q}$ is NOT invertible.

Thus, Incorrect Option.\\

\begin{align*}
    \boxed{\text{Only Option-A is Correct.}}
\end{align*}
\end{frame}

\end{document}