\documentclass{beamer}
\usepackage[utf8]{inputenc}

\usetheme{Madrid}
\usecolortheme{default}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{txfonts}
\usepackage{multicol}
\usepackage{tkz-euclide}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{tabularx}
\usepackage{gvv}
\usepackage{lmodern}
\usepackage{circuitikz}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{hyperref}

\setbeamertemplate{page number in head/foot}[totalframenumber]

\usepackage{tcolorbox}
\tcbuselibrary{minted,breakable,xparse,skins}



\definecolor{bg}{gray}{0.95}
\DeclareTCBListing{mintedbox}{O{}m!O{}}{%
  breakable=true,
  listing engine=minted,
  listing only,
  minted language=#2,
  minted style=default,
  minted options={%
    linenos,
    gobble=0,
    breaklines=true,
    breakafter=,,
    fontsize=\small,
    numbersep=8pt,
    #1},
  boxsep=0pt,
  left skip=0pt,
  right skip=0pt,
  left=25pt,
  right=0pt,
  top=3pt,
  bottom=3pt,
  arc=5pt,
  leftrule=0pt,
  rightrule=0pt,
  bottomrule=2pt,
  toprule=2pt,
  colback=bg,
  colframe=orange!70,
  enhanced,
  overlay={%
    \begin{tcbclipinterior}
    \fill[orange!20!white] (frame.south west) rectangle ([xshift=20pt]frame.north west);
    \end{tcbclipinterior}},
  #3,
}
\lstset{
    language=C,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    stringstyle=\color{orange},
    commentstyle=\color{green!60!black},
    numbers=left,
    numberstyle=\tiny\color{gray},
    breaklines=true,
    showstringspaces=false,
}
%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title %optional
{5.13.30}
\date{September 30,2025}
%\subtitle{A short story}

\author % (optional)
{Aditya Appana - EE25BTECH11004}



\begin{document}


\frame{\titlepage}
\begin{frame}{Question}
Let $\vec{A}$ be a square matrix all of whose entries are integers. Then which of the
following is true?
\begin{enumerate}
    \item If $det(\vec{A})\neq $ ±$1$, then $\vec{A}^{-1}$ exists but all its entries are not necessarily integers
    \item If $det(\vec{A})\neq $ ±$1$, then $\vec{A}^{-1}$ exists and all its entries are non-integers
    \item If $det(\vec{A}) = $ ±$1$, then $\vec{A}^{-1}$ exists but all its entries are integers
    \item If $det(\vec{A})= $ ±$1$, then $\vec{A}^{-1}$ need not exist

\end{enumerate}
\end{frame}



\begin{frame}[fragile]
    \frametitle{Solution}
We will proceed by checking each option.\\

\underline{A)}\\

Let us take a square matrix $\vec{A}$ having all integer entries. Let rows $R_1$ and $R_2$ be equal.
By performing row operation $R_1 \xrightarrow{} R_1 - R_2$, all elements in $R_1 $ become 0. Therefore, $|\vec{A}| = 0$. We know that if $|\vec{A}|= 0$, $\vec{A^{-1}}$ does not exist. Therefore, this option is wrong.\\

\end{frame}

\begin{frame}[fragile]
    \frametitle{Solution}
For example, consider a matrix $\vec{A}$ = \myvec{3&3&3\\3&3&3\\ 1&4&2}. $\vec{A}$ has only integer entries.
\begin{align*}
\myvec{3&3&3\\3&3&3\\ 1&4&2} \xrightarrow{\text{R_1 \rightarrow $R_1 - R_2$}} \myvec{0&0&0\\3&3&3\\ 1&4&2}
\end{align*}\\

Since $R_1$ consists of only 0's, $|\vec{A}|$ = 0. Hence $\vec{A}$ is not invertible.

\end{frame}

\begin{frame}[fragile]
    \frametitle{Solution}
\underline{B)}\\

For example, consider a matrix $\vec{A} = \myvec{2 & 1 \\ 2 & 2}$. $|\vec{A}| = 2$
\begin{align*}
    \vec{A^{-1}} = \frac{1}{2}\myvec{2 & -1 \\ -2 & 2} = \myvec{1 & -1/2 \\ 1 & 1}.
\end{align*}\\

This is a counterexample to the statement; hence, option \textbf{B} is wrong.

\end{frame}
\begin{frame}[fragile]
    \frametitle{Solution}

\underline{D)}\\

We know that if $|\vec{A}| \neq 0$, $\vec{A^{-1}}$ exists. By this logic, this option is wrong.\\

For example, consider a matrix $\vec{A}$ = $\myvec{\frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}} \\ \frac{-1}{\sqrt{2}} & \frac{1}{\sqrt{2}}}$. $|\vec{A}| = 1$, and since this is an orthogonal matrix, 
\begin{align*}
\vec{A^{-1}} = \vec{A^T} = \myvec{\frac{1}{\sqrt{2}} & \frac{-1}{\sqrt{2}} \\ \frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}}}. \end{align*}\\

$\vec{A^{-1}}$ exists, which is a contradiction to the statement in option \textbf{D}.
Therefore, the correct answer is \texbtf{C)}.
\end{frame}


\end{document}