\documentclass[journal]{IEEEtran}
\usepackage[a5paper, margin:10mm, onecolumn]{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{mathtools}
\usepackage{gvv-book}
\usepackage{gvv}
\usepackage{hyperref}

\begin{document}

\title{12.267}
\author{Puni Aditya - EE25BTECH11046}
\maketitle

\textbf{Question:}

Two matrices $\vec{A}$ and $\vec{B}$ are said to be similar if 
\begin{align*}
    \vec{B} = \vec{P}^{-1} \vec{A}\vec{P}
\end{align*}
for some invertible matrix $\vec{P}$. Which of the following statements is NOT TRUE?
\begin{enumerate}
    \item det $\vec{A}$ = det $\vec{B}$
    \item Trace of $\vec{A}$ = Trace of $\vec{B}$
    \item $\vec{A}$ and $\vec{B}$ have the same eigenvectors
    \item $\vec{A}$ and $\vec{B}$ have the same eigenvalues
\end{enumerate}

\textbf{Solution:}

Let $\vec{A}$ and $\vec{B}$ be similar matrices, such that 
\begin{align} 
    \vec{B} = \vec{P}^{-1}\vec{A}\vec{P}
\end{align}
for an invertible matrix $\vec{P}$. \\
For the determinant in 1),
\begin{align}
    \mydet{\vec{B}} &= \mydet{\vec{P}^{-1}\vec{A}\vec{P}} \\
    &= \mydet{\vec{P}^{-1}}\mydet{\vec{A}}\mydet{\vec{P}} \\
    &= \frac{1}{\mydet{\vec{P}}}\mydet{\vec{A}}\mydet{\vec{P}} = \mydet{\vec{A}}
\end{align}
The statement is true. \\
For the trace in 2), \\
The cyclic property of trace of matrices states 
\begin{align}
    \text{Tr}\brak{\vec{X}\vec{Y}\vec{Z}} = \text{Tr}\brak{\vec{Z}\vec{X}\vec{Y}} \label{eq:46}
\end{align}
Using \eqref{eq:46}
\begin{align}
    \text{Tr}\brak{\vec{B}} &= \text{Tr}\brak{\vec{P}^{-1}\vec{A}\vec{P}} \\
    &= \text{Tr}\brak{\vec{A}\vec{P}\vec{P}^{-1}} = \text{Tr}\brak{\vec{A}}
\end{align}
The statement is true. \\
For the eigenvalues in 4), we examine the characteristic polynomial.
\begin{align}
    \mydet{\vec{B} - \lambda\vec{I}} &= \mydet{\vec{P}^{-1}\vec{A}\vec{P} - \lambda\vec{I}} \\
    &= \mydet{\vec{P}^{-1}\vec{A}\vec{P} - \lambda\vec{P}^{-1}\vec{I}\vec{P}} \\
    &= \mydet{\vec{P}^{-1}\brak{\vec{A} - \lambda\vec{I}}\vec{P}} \\
    &= \mydet{\vec{P}^{-1}}\mydet{\vec{A} - \lambda\vec{I}}\mydet{\vec{P}} \\
    &= \mydet{\vec{A} - \lambda\vec{I}}
\end{align}
Since the characteristic polynomials are identical, the eigenvalues are the same. The statement is true. \\
For the eigenvectors in 3), let $\vec{v}$ be an eigenvector of $\vec{A}$ with eigenvalue $\lambda$, so that
\begin{align}
    \vec{A}\vec{v} = \lambda\vec{v}
\end{align}
\begin{align}
    \vec{B}\brak{\vec{P}^{-1}\vec{v}} &= \brak{\vec{P}^{-1}\vec{A}\vec{P}}\brak{\vec{P}^{-1}\vec{v}} \\
    &= \vec{P}^{-1}\vec{A}\brak{\vec{P}\vec{P}^{-1}}\vec{v} \\
    &= \vec{P}^{-1}\vec{A}\vec{v} = \vec{P}^{-1}\brak{\lambda\vec{v}} \\
    &= \lambda\brak{\vec{P}^{-1}\vec{v}}
\end{align}
This shows that if $\vec{v}$ is an eigenvector of $\vec{A}$, then $\vec{P}^{-1}\vec{v}$ is the eigenvector of $\vec{B}$ for the same eigenvalue. Since $\vec{v} \neq \vec{P}^{-1}\vec{v}$ in general, the eigenvectors are not the same. The statement is not true. \\
\textbf{Example:} Let
\begin{align}
    \vec{A} = \myvec{1 & 1 \\ 0 & 2}, \quad \vec{P} = \myvec{1 & 1 \\ 0 & 1} \implies \vec{P}^{-1} = \myvec{1 & -1 \\ 0 & 1}
\end{align}
The matrix $\vec{A}$ has an eigenvalue $\lambda=2$ with corresponding eigenvector 
\begin{align}
	\vec{v} = \myvec{1 \\ 1}
\end{align}
The similar matrix $\vec{B}$ is
\begin{align}
    \vec{B} = \vec{P}^{-1}\vec{A}\vec{P} = \myvec{1 & -1 \\ 0 & 1}\myvec{1 & 1 \\ 0 & 2}\myvec{1 & 1 \\ 0 & 1} = \myvec{1 & 0 \\ 0 & 2}
\end{align}
The corresponding eigenvector of $\vec{B}$ for the eigenvalue $\lambda=2$ is 
\begin{align}
	\vec{w} = \vec{P}^{-1}\vec{v}
\end{align}
\begin{align}
    \vec{w} = \myvec{1 & -1 \\ 0 & 1}\myvec{1 \\ 1} = \myvec{0 \\ 1}
\end{align}
Clearly, $\vec{v} \neq \vec{w}$. \\
The statement that is NOT TRUE is \textbf{3) $\vec{A}$ and $\vec{B}$ have the same eigenvectors}.

\end{document}
